---
title: "１２１１"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# CATEGORICAL DATA MANIPULATION ----

# 1.0 Factor Basics ----

# What is a Factor?
# A way of managing categorical data

# Why do we want factors? 
# 1. Can group numeric values into bin (think price = low, medium, high)
# 2. Can reorder categories for visualization (fct_reorder)
# 3. Can manipulate categories much eaiser (fct_lump)
# 4. Machine learning and modeling algorithms may require factor data type for categorical data. 

```{r}
rm(list=ls())
install.packages("pacman")
pacman::p_load(tidyverse, lubridate, tidyquant)
pacman::p_load(timetk)
library(pacman)
library(tidyverse)
library(lubridate)
library(tidyquant)
```

```{r}
bike_orderlines_tbl <- readRDS("bike_orderlines.rds")
```

# 2.0 Motivating Example -----
#Manipulation

```{r}

sales_by_cat_2_tbl <- bike_orderlines_tbl %>%
  select(category_2, total_price) %>%
  group_by(category_2) %>%
  summarise(sales=sum(total_price)) %>%
  ungroup() %>%
  
  arrange(desc(sales)) %>%
  mutate(category_2 = category_2 %>% as_factor(),
         value      = as.numeric(category_2))
```

# Plotting

```{r}
sales_by_cat_2_tbl %>%
  ggplot(aes(x = sales, y = category_2)) +
  geom_point(size = 5, color = "red") +
  labs(title = "Sales By Category 2") +
  scale_x_continuous(labels = scales::dollar_format()) +
  theme_tq() +
  expand_limits(x = 0)
```

```{r}
plot_sales <- function(data) { 
  data %>%
    ggplot(aes(x = sales, y = category_2)) +
    geom_point(size = 5, color = "red") +
    labs(title = "Sales By Category 2") +
    scale_x_continuous(labels = scales::dollar_format()) +
    theme_tq() +
    expand_limits(x = 0)
}

sales_by_cat_2_tbl %>% plot_sales()
```

# 3.0 Forcats Basics ----
# 3.1 Inspecting Factors ----

# Vector

```{r}
sales_by_cat_2_tbl %>% pull(category_2)
```
# Tibble
```{r}
sales_by_cat_2_tbl %>%
  mutate(category_2 = category_2 %>% fct_rev() %>% fct_rev())

sales_by_cat_2_tbl %>% pull(category_2) %>% levels()

sales_by_cat_2_tbl %>% pull(category_2) %>% as.numeric()
```

# Tibble

```{r}
sales_by_cat_2_tbl %>%
  mutate(category_2 = category_2 %>% fct_rev() %>% fct_rev()) %>%
  mutate(
    label = category_2 %>% as.character(),
    value = category_2 %>% as.numeric()
  )
```

# 3.2 Creating Factors: as_factor() vs as.factor() ----
# as.factor() - alphabetical order

```{r}
sales_by_cat_2_tbl %>%
  mutate(
    category_2           = as.character(category_2),
    category_2_as_factor = as_factor(category_2) %>% as.numeric(),
    category_2_as.factor = as.factor(category_2) %>% as.numeric()
  )
```

# 3.3 Reordering Factors: fct_reorder() and fct_rev() ----

```{r}
sales_by_cat_2_tbl %>%
  arrange(desc(sales)) %>%
  mutate(sales_negative = -sales) %>%
  mutate(
    category_2 = category_2 %>% fct_reorder(sales_negative),
    values     = category_2 %>% as.numeric()
    ) %>%
  
  plot_sales()
```

# 3.4 Time-Based Reordering: fct_reorder2() ----

```{r}
sales_by_cat_2_q_tbl <- bike_orderlines_tbl %>%
  mutate(order_date = order_date %>% floor_date("quarter") %>% ymd())%>%
  group_by(category_2, order_date)%>%
  summarise(sales = sum(total_price)) %>%
  ungroup()

sales_by_cat_2_q_tbl
```
#fct_reorder2　ｔｉｍｅ　ｓｅｒｉｅｓ

```{r}
sales_by_cat_2_q_tbl %>%
  mutate(category_2 = category_2 %>% fct_reorder2(order_date, sales)) %>%
  ggplot(aes(x = order_date, y = sales, color = category_2)) +
  geom_point() +
  geom_line()+
  theme_tq() +
  scale_color_tq() +
  facet_wrap(~ category_2) +
  
  scale_y_continuous(labels = scales::dollar_format(scale = 1e-6, suffix = "M"))
```

# 3.5 Creating "Other" Category - fct_lump() & fct_relevel() ----

```{r}
sales_by_cat_2_tbl %>%
  
  mutate(category_2 = category_2 %>% fct_lump(n = 6, 
                                              w = sales, 
                                              other_level = "All Other Bike Categories")) %>%
  
  group_by(category_2) %>%
  summarize(sales = sum(sales)) %>%
  
  mutate(category_2 = category_2 %>% fct_relevel("All Other Bike Categories", after = 0)) %>%
  
  plot_sales()
```